Longitudinal Data Analysis with the ABCD Study

### 2024-03-18 index.qmd
update

---
#title: "Longitudinal Analysis"

format:
  html:
    css: styles.css
    #theme: cosmo
    page-layout: custom
    grid:
      sidebar-width: 200px
      body-width: 2000px
      margin-width: 0px
      gutter-width: 0rem
---

Test

>>>>

---
title: "Longitudinal Data Analysis with the ABCD Study"
format:
  html:
    #css: styles.css
    theme: cosmo
    #page-layout: custom
    #grid:
      #sidebar-width: 200px
      #body-width: 2000px
      #margin-width: 0px
      #gutter-width: 0rem
---

# Welcome to the Longitudinal Data Analysis Project

## Our Mission

This ongoing project is guided by the Biostatistics Working Group of the [Adolescent Brain Cognitive Development (ABCD) Study](https://abcdstudy.org/). The aim is to provide accessible resources for those interested in longitudinal data analysis and related methodologies. We provide practial [examples and tutorials](https://opendevsci.github.io/LongDev-ABCD/examples/examples.html) to demonstrate different longitudinal methodologies/techniques using publically available data from the ABCD Study.

::: {.callout-important}
NOTE: This project is in beta and as such is still very much a work in progress. At present, [Examples](https://opendevsci.github.io/LongDev-ABCD/examples/examples.html) should NOT be considered "ready-to-use". However, avaiable code snippets in each of the examples may still prove useful to guide your own analysis. We very much welcome feedback and contributions from the community to help us expand and improve our resources. Please see our [GitHub repository](https://github.com/OpenDevSci/LongDev-ABCD) and our [Contribution Guide](https://github.com/OpenDevSci/LongDev-ABCD/blob/main/docs/Contributing.md) for more information on how to contribute.
:::

## Why This Project?

- **Publicly Available Code**: We (will) provide ready-to-use code examples to aid in your research and studies.
- **Open Source Collaboration**: Join our community to contribute, learn, and share knowledge on longitudinal data analysis.
- **Educational Resource**: Whether you're looking to understand GitHub, R, RMarkdown/Quarto, or longitudinal analysis methods, we're here to help.

## How to Contribute

1. **Provide New Examples**: Share your knowledge by contributing new analysis examples.
2. **Help With Documentation**: Assist in enhancing our project documentation for better user understanding.
3. **Repository Maintenance**: Support the upkeep of our GitHub repository to ensure it remains an accessible resource for all.

Interested in contributing? Check out our [Contribution Guide](https://github.com/OpenDevSci/LongDev-ABCD/blob/main/docs/Contributing.md) for more details.

## Project Resources

- **Code Examples**: Explore this website and our [GitHub Repository](https://github.com/OpenDevSci/LongDev-ABCD) for a range of analysis examples.
- **Documentation**: Dive into our [Project Board](https://github.com/orgs/OpenDevSci/projects/13) for detailed insight into ongoing project tasks and timelines.
- **Community**: Join our [Discussion Forum](https://github.com/orgs/OpenDevSci/discussions) to connect with other community members.

## About Us

We're passionate about making longitudinal data analysis accessible and understandable. While we're not experts in every area, we believe in the power of community and open source collaboration to expand knowledge and skills in these essential research methodologies.

**Let's make data analysis more approachable together.**
